---
format:
  html:
    code-fold: true
filters:
  - rich-iannone/quarto-email
editor_options: 
  chunk_output_type: console
---


## Goals

The goal of this document is to demonstrate different conditional
outcomes in rendering reports on Posit Connect:


## Setup

### Load required packages

```{r}
#| warning: false
#| message: false
library(tidyverse)
library(glue)
```

## Generate Conditional Outcome

For demonstration, let's define 4 possible outcomes:

-   **case 1** - Send an email with a cat picture
-   **case 2** - Send an email with a dog picture
-   **case 3** - Do not send any emails but still render this notebook
    completely


```{r}
# randomly select a case 1, 2, or 3
case <- sample(1:3, 1) 
```

For this rendering, it's going to be:

<h3>case `r case`!</h3>

## Render emails (if appropriate)

```{r}
if(case == 1){
  send_email = TRUE
  subject = glue("🐈 Meow! Here's the cat of the day for {wday(today(), label = TRUE, abbr = FALSE)}")
  body = "boring plain text."
}else if(case == 2){
  send_email = TRUE
  subject = glue("🐕 Woof! It's {wday(today(), label = TRUE, abbr = FALSE)}, here's a pup!")
  body = "i wish i could format this."
}else if(case == 3){
  send_email = FALSE
  subject = "N/A - no email generated"
  body = NA
}
```

::: {.email}

`r body`

::: {.subject}
`r subject`
:::

::: {.email-scheduled}
`r send_email`
:::

:::



## Logging

Case: `r case`

Report run: `r Sys.time()`

Email sent? `r send_email`

Subject: `r subject`

Body: `r body`
